The mass relations between supermassive black holes and their host galaxies at $1< z<2$ with \hst-WFC3

### 2019-03-20 manuscript/manuscript.tex
Updating the comparing CANDLES figures.

The tight correlation between the mass of a supermassive black hole (\mbh) and its host galaxies properties indicates a connection of their evolution. The key to test this co-evolution scenario is to trace their correlation to more distant Universe. We measure using a sample of 32 X-ray-selected broad-line (type-1) AGN at $1.2<z<1.7$ in deep survey fields obtained with the {\it Hubble Space Telescope} (\hst). %Wide-Field Camera 3.
The high-resolution \hst\ images enable us to decompose the AGN image and infer the host properties including luminosity (\lhost) and stellar mass (\smass) in each case. The lower nuclear-to-host ratios and multi-band images of our samples provide accurate host properties.
The estimation of \mbh\ is based on our published near-infrared spectroscopic observations of the broad \halpha~and \hbeta~emission lines, which avoids the systemic bias by the \Civ\ or \Mgii\ lines. We compare the \mbh-\lhost~and \mbh-\smass~relation to the local active galaxies while taking the selection effect into account thus establishing the cosmic evolution in these relations. Considering the passive luminosity effect, we inferred a positive evolution of \mbh-\lhost, indicating that the BHs at higher redshift resides in less luminous galaxies than today. The \mbh-\smass\ of our high redshift sample is consistent with the local \mbh-\smass$_{\rm bluge}$ relations. Considering that our sample are composed of bulge and disk components, we are forced to concluded that our results consistent to a scenario that the growth of the black hole predates that of the bulge.
\end{abstract}

@@

\subsection{Comparison sample}
\textcolor{blue}{
We aim to collect the \mbh-\lhost\ and \mbh-\smass\ relations of our samples and comparing to the ones at different redshift. 
For calibrating with the local relation, we use the local AGN measurements by \citet{Ben++10} and \citet{Bennert++2011} (hereafter, B10 and B11a) to define our zero-point. The sample by B10 consistent 19 \mbh-\lhost\ relations with reliable \mbh\ measured using reverberation-mapped (uncertainty level $\sim0.15$ dex). The work of B11 contain 25 \mbh-\smass\ local active AGN analysis, where the \mbh\ are measured from single-epoch method (\mbh\ uncertainty level $\sim0.4$ dex). To increase the local \smass\ and \mbh\ to higher range, we also include the inactive galaxies (mainly ellipticals or S0) as done by \citet{H+R04}. It is worth note that in the local comparison sample, the bulge mass is equivalent to the total stellar mass for the local comparison sample. In other words, it is the local \mbh-\smass$_{Bulge}$ relation that we compared. }

@@

\subsection{Host galaxy properties}
We derive the rest-frame R band magnitude and luminosity of our sample based on their filter magnitude obtained last section. 18/32 systems have multi-band host magnitude which ables us to select the best stellar population that could fit to the overall sample. We find that the 1 Gyr stellar population with solar metallicity by Chabrier initial mass function (IMF) \citep{Bruzual2003} could well match the color between the WFC3 and ACS band magnitude of these sample. Adopting this stellar population, we perform the K-correction and derive the rest-frame R band magnitude of our sample. We further derive the rest-frame R band luminosity by $\log L_R/L_{R, \odot} = 0.4 (M_{R, \odot}-M_R)$, where $M_{R, \odot}=4.61$ \citep{Blanton07}. We estimate of the stellar mass content of each host galaxy by adopt the mass-to-light ratio (M/L) based on the stellar population we adopted.

@@

The inferred $L_R$ and $M_*$ are listed in Table~\ref{tab:result_sersic}. In the rest of this section, we compare them to the \mbh.

\subsection{\mbh-\lhost\ relation}
We show our measurements of the \mbh-\lhost\ relation together with the comparison sample in Figure~\ref{fig:ML}, panel (a). Following common practice, we fit the local relation as a linear relation,
\begin{eqnarray}
\label{eq:MLlocal}
\log \big( \frac{\mathcal M_{\rm BH}}{10^{7}M_{\odot}})= \alpha + \beta \log(\frac{L_R}{10^{10}L_{\odot}}),
\end {eqnarray}
which enables a direct comparison to the distant sample. The figure shows that the observed \mbh-\lhost\ relation for our measurements  are nearly identical to the local and intermediate ones, indicating that the black hole mass and the host luminosity located at a similar relation at different galaxy age. However, considering that both the black hole and host galaxy are expected to evolve over cosmic time, it is essential to transfer high-$z$ measurements to their values at today so as to compare them in an equivalent frame. Especially, in a passive evolution scenario, we expect \lhost\ to fade over time.

We follow \citet{Ding2017b} and parametrize the luminosity evolution with the functional form as
$d{\rm mag}_{\rm R} \sim d\log(1+z)$, i.e.,
\begin{eqnarray}
\label{eq:L_relation}
\log(L_{R,0})=\log(L_{R}) - 1.48 \log (1+z).
\end{eqnarray} 
This formulism is more accurate to fit a broad range redshift comparing to a single slope as $d$mag$/dz$. We refer to the \citet[][section 5.4]{Ding2017b} for more details. Transfering the \lhost\ to today, we show the evolution-corrected \mbh-\lhost\ relation in Figure~\ref{fig:ML}, panel (b) and find that, at fixed \mbh, the BH in the more distant universe tends to reside in less luminous hosts.

@@

Given that the current result does not take into account selection effects yet, we will draw the conclusion in the section~\ref{select_eff}

\subsection{\mbh-\smass\ relation}
Analyzing the correlation of the \mbh-\smass\ would be more efficient to help directly understand the connection between their coevolution. In Figure~\ref{fig:MM}, we plot the \mbh-\smass\ relation and compare to the local and intermediate sample. We visually see that the mass distributions for three samples are very similar. Similarly, we consider the local as linear relation to fit offset (i.e., $\Delta\log \mathcal M_{\rm BH}$) as a function of $\gamma \log (1 + z)$. We obtain the $\gamma  = 0.49 \pm 0.19$ which slightly indicates as the positive, see Figure~\ref{fig:MM-vz}, panel (a). In the of Figure~\ref{fig:MM-vz}, panel (b), we also show the ratio of \mbh-\smass of the three sample at different redshift. We highlight that our results are less biased in both the measurement of \mbh\ and \smass.

We highlight that the local sample employed are bulge dominated galaxies and the adopted \smass\ are equivalent to their bulge masses. That is, we are comparing the \mbh-\smass$_{,total}$ at distant universe to the \mbh-\smass$_{,bulge}$ at the local. Considering that a major part of the distant systems have indicated the disk component (i.e., the systems with fitted \sersic\ index close to 1), the \smass$_{,bluge}$ of them are supposed to be even less.

@@

\section{discussion}
\label{sec:dis}
\subsection{Systematic error}
In our analysis, we adopt one stellar population to the overall sample. We note that adopting the private stellar populations for these sample which have both multi-band host magnitude could be more robust in principle. However, considering that the host magnitude in ACS band are faint (host-total flux ratio $< 30\%$), the fidelity of the SED fitting is actually lost. Perhaps the best way to derive the stellar population is to combining our measurements to the ground-based photometry. \textcolor{red}{Describe the ground-based data}. In this paper, we focus on the decomposing of the AGN and carry out a rapid analysis of the \mbh-host raltions. The measurements incorporating the ground-based photometry and the comparison with the simulations are presented in our companion paper.

\subsection{Comparison with the inactive galaxies}
To understand how the AGNs activity affect their galaxies's morphology, we compared the 32 host measurements to the inactive galaxies in CANDLES imaging survey. We select 4401 inactive galaxies in a comparable redshift range ($1.2<z<1.7$) from the CANDLES-COSMOS catalog. Their \sersic\ properties are inferred by \citet{VDwel++2012} by \galfit, and their stellar mass are derived by 3-D-HST spectroscopic survey \citep{Momcheva2016, Brammer2012}.

We compare the \smass-\Reff\ relations in Figure~\ref{fig:Mstar-rn}. The inference shows that our AGN host are located at a higher end of the stellar mass.

@@

\begin{deluxetable*}{ccccccc}
\tablecolumns{7}
\tablewidth{0pt}
\tablecaption{The host inference of CID1174} 
\tablehead{ 
\colhead{PSF rank} &
\colhead{total $\chi ^2$} & 
\colhead{weights $w_i$} &
\colhead{host flux (counts)} &
\colhead{host flux ratio}&
\colhead{\Reff (arcsec)}&
\colhead{\sersic\ $n$}
 \\ 
\colhead{(1)} &
\colhead{(2)} &
\colhead{(3)} &
\colhead{(4)} &
\colhead{(5)} &
\colhead{(6)} &
\colhead{(7)} 
} 
\startdata
%\multicolumn{5}{c}{Sample presented in \citet{Treu+07}}\\
%\\
1 & $8584.429$ & $1.000$ & $82.209$ & $35.4\%$ & $0\farcs{}345$ & $1.114$ \\
2 & $8646.711$ & $0.920$ & $99.102$ & $41.9\%$ & $0\farcs{}298$ & $1.932$ \\
3 & $8816.947$ & $0.734$ & $76.74$ & $33.0\%$ & $0\farcs{}365$ & $1.102$ \\
4 & $9304.841$ & $0.383$ & $128.618$ & $54.7\%$ & $0\farcs{}231$ & $2.78$ \\
5 & $9652.575$ & $0.241$ & $187.498$ & $79.0\%$ & $0\farcs{}116$ & $6.175$ \\
6 & $9917.101$ & $0.170$ & $100.166$ & $42.3\%$ & $0\farcs{}287$ & $2.066$ \\
7 & $10018.324$ & $0.148$ & $75.061$ & $32.3\%$ & $0\farcs{}365$ & $1.226$ \\
8 & $10087.456$ & $0.135$ & $79.835$ & $34.3\%$ & $0\farcs{}358$ & $1.195$ \\
\hline\\
Weighted value & & & $97.322\pm28.336$ & $41.5\%\pm11.7\%$& $0\farcs{}309\pm0\farcs{}065$  & $1.862\pm1.26$  \\
\enddata
\label{tab:weight_CID1174}
\tablecomments{
Column~1: Rank of the PSF from the library.
Column~2: Total $\chi ^2$ for the corresponding PSF.
Column~3: Weights for the inference.
Column~4-7: Fitted value for the host flux, host/total flux ratio, effective radius, and \sersic\ index.
For this sample, the inflation parameter $\alpha$ calculated by Eq.~\ref{eq:alpha} is 16.671.
}
\end{deluxetable*}

@@

\colhead{reduced $\chi ^2$}& \colhead{host-to-total flux ratio}& 

@@

\colhead{reduced $\chi ^2$}& \colhead{host-to-total flux ratio}& \colhead{magnitude} &

@@

CID1174 & $2.307$ & $41.5\%\pm11.7\%$ & $0\farcs{}31\pm0\farcs{}07$ & $1.86\pm1.26$ & $21.48\substack{+0.37\\-0.28}$ & $2.496$ & $11.2\%\pm1.1\%$ & $23.21\substack{+0.11\\-0.10}$ & $11.13$ &$10.85$\\
CID1281 & $1.322$ & $49.3\%\pm13.7\%$ & $0\farcs{}24\pm0\farcs{}09$ & $3.15\pm1.48$ & $22.88\substack{+0.36\\-0.27}$ & $1.378$ & $18.5\%\pm7.7\%$ & $24.83\substack{+0.60\\-0.38}$ & $10.49$ &$10.21$\\
CID206 & $2.054$ & $35.3\%\pm24.3\%$ & $0\farcs{}29\pm0\farcs{}15$ & $3.07\pm2.48$ & $21.82\substack{+1.30\\-0.58}$ & $1.903$ & $7.7\%\pm2.4\%$ & $23.67\substack{+0.40\\-0.29}$ & $10.95$ &$10.66$\\
CID216 & $1.514$ & $93.9\%\pm4.7\%$ & $0\farcs{}25\pm0\farcs{}06$ & $6.16\pm1.21$ & $21.51\substack{+0.05\\-0.05}$ & $1.425$ & $35.1\%\pm1.5\%$ & $23.45\substack{+0.05\\-0.05}$ & $11.13$ &$10.85$\\
CID237 & $2.349$ & $29.9\%\pm6.3\%$ & $0\farcs{}87\pm0\farcs{}17$ & $4.74\pm1.70$ & $21.28\substack{+0.26\\-0.21}$ & $2.354$ & $3.2\%\pm2.0\%$ & $23.72\substack{+1.04\\-0.52}$ & $11.26$ &$10.98$\\
CID255 & $1.625$ & $18.9\%\pm5.4\%$ & $0\farcs{}19\pm0\farcs{}06'$ & $4.21\pm1.49$ & $21.61\substack{+0.37\\-0.28}$ & 2.858 & $4.2\%\pm1.8\%$ & $22.89\substack{+0.60\\-0.39} $& $11.17$ & $10.89$\\
CID3242 & $2.751$ & $46.1\%\pm12.7\%$ & $0\farcs{}20\pm0\farcs{}16$ & $6.14\pm1.87$ & $21.16\substack{+0.35\\-0.26}$ & $2.596$ & $4.8\%\pm1.3\%$ & $23.60\substack{+0.34\\-0.26}$ & $11.25$ &$10.97$\\
CID3570 & $1.665$ & $76.5\%\pm1.6\%$ & $0\farcs{}70\pm0\farcs{}01$ & $0.73\pm0.05$ & $21.16\substack{+0.02\\-0.02}$ & $1.332$ & $85.6\%\pm1.5\%$ & $22.97\substack{+0.01\\-0.01}$ & $11.07$ &$10.79$\\
CID452 & $1.684$ & $75.4\%\pm3.9\%$ & $0\farcs{}37\pm0\farcs{}02$ & $1.40\pm0.18$ & $21.18\substack{+0.06\\-0.06}$ & $1.452$ & $37.8\%\pm0.7\%$ & $22.73\substack{+0.02\\-0.02}$ & $11.21$ &$10.93$\\
CID454 & $2.203$ & $35.8\%\pm2.5\%$ & $0\farcs{}39\pm0\farcs{}02$ & $0.62\pm0.11$ & $21.20\substack{+0.08\\-0.07}$ & $1.291$ & $9.2\%\pm0.5\%$ & $23.35\substack{+0.06\\-0.06}$ & $11.19$ &$10.91$\\
CID50 & $5.576$ & $16.5\%\pm9.0\%$ & $0\farcs{}16\pm0\farcs{}11$ & $3.22\pm2.22$ & $20.93\substack{+0.86\\-0.48}$ & $4.940$ & $5.0\%\pm3.3\%$ & $22.50\substack{+1.15\\-0.55}$ & $11.15$ &$10.87$\\
CID543 & $1.902$ & $30.6\%\pm9.7\%$ & $0\farcs{}10\pm0\farcs{}00$ & $0.49\pm0.33$ & $21.99\substack{+0.41\\-0.30}$ & $1.435$ & $5.2\%\pm2.0\%$ & $23.77\substack{+0.53\\-0.36}$ & $10.79$ &$10.51$\\
CID597 & $1.565$ & $42.4\%\pm16.6\%$ & $0\farcs{}17\pm0\farcs{}06$ & $1.75\pm0.78$ & $21.87\substack{+0.54\\-0.36}$ & $1.254$ & $11.5\%\pm1.3\%$ & $23.56\substack{+0.13\\-0.11}$ & $10.81$ &$10.53$\\
CID607 & $1.692$ & $43.6\%\pm17.9\%$ & $0\farcs{}21\pm0\farcs{}09$ & $3.42\pm1.10$ & $21.19\substack{+0.58\\-0.37}$ & $2.590$ & $4.7\%\pm1.8\%$ & $23.57\substack{+0.51\\-0.35}$ & $11.10$ &$10.82$\\
CID70 & $2.041$ & $19.7\%\pm4.9\%$ & $0\farcs{}42\pm0\farcs{}10$ & $3.62\pm1.03$ & $21.86\substack{+0.30\\-0.24}$ & $2.361$ & $2.3\%\pm1.1\%$ & $24.63\substack{+0.68\\-0.41}$ & $11.07$ &$10.79$\\
LID1273 & $1.697$ & $53.3\%\pm9.1\%$ & $0\farcs{}30\pm0\farcs{}04$ & $1.22\pm0.49$ & $20.94\substack{+0.21\\-0.18}$ & $2.137$ & $6.4\%\pm0.8\%$ & $23.29\substack{+0.15\\-0.13}$ & $11.40$ &$11.12$\\
LID1538 & $2.362$ & $43.5\%\pm7.8\%$ & $0\farcs{}18\pm0\farcs{}04$ & $2.82\pm0.48$ & $21.25\substack{+0.22\\-0.18}$ & $2.173$ & $7.5\%\pm1.2\%$ & $23.09\substack{+0.19\\-0.16}$ & $11.21$ &$10.93$\\
LID360 & $3.918$ & $18.4\%\pm2.0\%$ & $0\farcs{}63\pm0\farcs{}02$ & $0.75\pm0.36$ & $21.46\substack{+0.14\\-0.12}$ & $4.914$ & $3.7\%\pm0.5\%$ & $23.25\substack{+0.17\\-0.15}$ & $11.17$ &$10.88$\\
XID2138 & $1.597$ & $38.9\%\pm5.5\%$ & $0\farcs{}50\pm0\farcs{}03$ & $1.24\pm0.39$ & $21.87\substack{+0.17\\-0.15}$ & $2.731$ & $5.0\%\pm1.3\%$ & $23.90\substack{+0.31\\-0.24}$ & $10.98$ &$10.70$\\
XID2202 & $3.23$ & $33.3\%\pm8.0\%$ & $0\farcs{}10\pm0\farcs{}00$ & $3.96\pm1.02$ & $21.16\substack{+0.30\\-0.24}$ & $3.852$ & $8.3\%\pm1.9\%$ & $22.59\substack{+0.29\\-0.23}$ & $11.24$ &$10.96$\\
XID2396 & $3.669$ & $23.9\%\pm10.5\%$ & $0\farcs{}58\pm0\farcs{}09$ & $0.77\pm1.36$ & $21.40\substack{+0.65\\-0.40}$ & $5.346$ & $2.3\%\pm0.5\%$ & $23.36\substack{+0.24\\-0.20}$ & $11.20$ &$10.92$\\

>>>>

The tight correlations between the mass of a supermassive black hole (\mbh) and its host galaxy properties suggests an evolutionary connection. A powerful way to test this co-evolution hypothesis is to trace the correlations back in cosmic time. For this purpose, we obtained multi-band {\it Hubble Space Telescope} of  a sample of 32 X-ray-selected broad-line (type-1) AGN at $1.2<z<1.7$ (look-back time 8-10 Gyrs). By applying state-of-the art tools to the images we obtained accurate host galaxy luminosity and stellar mass. The black hole mass (\mbh) is based on published near-infrared spectroscopic observations of the broad \halpha~and \hbeta~emission lines, which avoids potential unknown systematic uncertainties associated with the less well calibrated UV lines \Civ\ or \Mgii, commonly used at these redshifts. We compare the \mbh-\lhost~and \mbh-\smass~relations to those of local active galaxies, accounting for selection effects, to infer their evolution. The \mbh-\lhost relation is inconsistent with the local one, accounting for passive evolution, indicating that the BHs at higher redshift resides in less luminous galaxies than today. The \mbh-\smass\ of our high redshift sample is consistent with the local \mbh-\smass$_{\rm bluge}$ relations. Considering that our sample are composed of bulge and disk components, we are forced to concluded that our results consistent to a scenario that the growth of the black hole predates that of the bulge.
\end{abstract}

@@

\subsection{Comparison sample}
\textcolor{blue}{
We aim to collect the \mbh-\lhost\ and \mbh-\smass\ relations of our samples and comparing to the ones at different redshift. 
For calibrating with the local relation, we use the local AGN measurements by \citet{Ben++10} and \citet{Bennert++2011} (hereafter, B10 and B11a) to define our zero-point. The sample by B10 consistent 19 \mbh-\lhost\ relations with reliable \mbh\ measured using reverberation-mapped (uncertainty level $\sim0.15$ dex). The work of B11 contains 25 \mbh-\smass\ local active AGN analysis, where the \mbh\ are measured from the single-epoch method (\mbh\ uncertainty level $\sim0.4$ dex). To increase the local \smass\ and \mbh\ to the higher range, we also include the inactive galaxies (mainly ellipticals or S0) as done by \citet{H+R04}. It is worth note that in the local comparison sample, the bulge mass is equivalent to the total stellar mass for the local comparison sample. In other words, it is the local \mbh-\smass$_{Bulge}$ relation that we compared. }

@@

\subsection{Host galaxy properties}
We derive the rest-frame R band magnitude ($M_R$) and luminosity ($L_R$) of our sample based on their filter magnitude. 18/32 systems have multi-band host magnitude which ables us to select the best stellar population that could fit the overall sample. We find that the 1~Gyr stellar population with solar metallicity by Chabrier initial mass function (IMF) \citep{Bruzual2003} could well match the color between the WFC3 and ACS band magnitude of these samples. Adopting the color information, we perform the K-correction and derive the rest-frame R band magnitude of our sample. Given that the WFC3 filter we selected is very close to the rest-frame R band, we expect the $M_R$ uncertainty level raised by this K-correction is within 0.05~mag. We derive the rest-frame R band luminosity by $\log L_R/L_{R, \odot} = 0.4 (M_{R, \odot}-M_R)$, where $M_{R, \odot}=4.61$ \citep{Blanton07}.

Taking the stellar population, we estimate the stellar mass content of each host galaxy according to the mass-to-light ratio of the stellar population we adopted. The raised uncertainty level to the stellar mass is expected to be within 0.1~dex.

@@

The inferred $L_R$ and $M_*$ are listed in Table~\ref{tab:result_sersic}. In the rest of this section, we compare their relations to to the \mbh.

\subsection{\mbh-\lhost\ relation}
We show our measurements of the \mbh-\lhost\ relation together with the comparison sample in Figure~\ref{fig:ML}, panel (a). Following common practice, we fit the local relation as a linear relation,
\begin{eqnarray}
\label{eq:MLlocal}
\log \big( \frac{\mathcal M_{\rm BH}}{10^{7}M_{\odot}})= \alpha + \beta \log(\frac{L_R}{10^{10}L_{\odot}}),
\end {eqnarray}
which enables direct comparison to the distant sample. The figure shows that the observed \mbh-\lhost\ relation for our measurements is nearly identical to the local and intermediate ones, indicating that the black hole mass and the host luminosity located at a similar relation at different galaxy age. However, considering that both the black hole and host galaxy are expected to evolve over cosmic time, it is essential to transfer high-$z$ measurements to their values at today so as to compare them in an equivalent frame. Especially, in a passive evolution scenario, we expect \lhost\ to fade over time.

We follow \citet{Ding2017b} and parametrize the luminosity evolution with the functional form as
$d{\rm mag}_{\rm R} \sim d\log(1+z)$, i.e.,
\begin{eqnarray}
\label{eq:L_relation}
\log(L_{R,0})=\log(L_{R}) - 1.48 \log (1+z).
\end{eqnarray} 
This formalism is more accurate to fit a broad range redshift comparing to a single slope as $d$mag$/dz$. We refer to \citet[][section 5.4]{Ding2017b} for more details. Transferring the \lhost\ to today, we show the evolution-corrected \mbh-\lhost\ relation in Figure~\ref{fig:ML}, panel (b) and find that, at fixed \mbh, the BH in the more distant universe tends to reside in less luminous hosts.

@@

Given that the current result does not take into account selection effects yet, we will draw the conclusion in section~\ref{select_eff}.

\subsection{\mbh-\smass\ relation}
Analyzing the correlation of the \mbh-\smass\ would be more efficient to help directly understand the connection between their coevolution. In Figure~\ref{fig:MM}, we plot the \mbh-\smass\ relation and compare to the local and intermediate sample. We visually see that the mass distributions for the three samples are very similar. Similarly, we consider the local as linear relation to fit offset (i.e., $\Delta\log \mathcal M_{\rm BH}$) as a function of $\gamma \log (1 + z)$. We obtain the $\gamma  = 0.49 \pm 0.19$ which slightly indicates as the positive, see Figure~\ref{fig:MM-vz}, panel (a). We also show the ratio of \mbh-\smass of the three samples at different redshift in Figure~\ref{fig:MM-vz}, panel (b). We highlight that our results are less biased in both the measurement of \mbh\ and \smass.

We highlight that the local sample employed are bulge-dominated galaxies and the adopted \smass\ are equivalent to their bulge masses. That is, we are comparing the \mbh-\smass$_{,total}$ at the distant universe to the \mbh-\smass$_{,bulge}$ at the local. Considering that a major part of the distant systems has indicated the disk component (i.e., the systems with fitted \sersic\ index close to 1), the \smass$_{,bluge}$ of them are supposed to be even less.

@@

\section{discussion}
\label{sec:dis}
\subsection{Systematic error}
In our analysis, we adopt one stellar population to the overall sample. We note that adopting the private stellar populations for these samples which have both multi-band host magnitude could be more robust in principle. However, considering that the host magnitude in ACS band is faint (host-total flux ratio $< 30\%$), the fidelity of the SED fitting is actually lost. Perhaps the best way to derive the stellar population is to combining our measurements to the ground-based photometry. \textcolor{red}{Describe the ground-based data}. In this paper, we focus on the decomposing of the AGN and carry out a rapid analysis of the \mbh-host relations. The measurements incorporating the ground-based photometry and the comparison with the simulations are presented in our companion paper.

\subsection{Comparison to the inactive galaxies}
To understand whether AGNs activity affects their galaxies' morphology, we compared the 32 host measurements to the inactive galaxies in CANDLES imaging survey. We select 4401 inactive galaxies in a comparable redshift range ($1.2<z<1.7$) from the CANDLES-COSMOS catalog. Their \sersic\ properties are inferred by \citet{VDwel++2012} by \galfit, and their stellar masses are derived by 3-D-HST spectroscopic survey \citep{Momcheva2016, Brammer2012}.

\textcolor{blue}{ Description and comments to be written}:
We show the \smass-\Reff\ relations and \smass-\sersic\ n in Figure~\ref{fig:Mstar-rn}. 
The comparison the histogram of \Reff\ and \sersic\ n are shown in Figure~\ref{fig:hist_rn}.

%high
%The distribution shows that our AGN host are located at a higher end of the stellar mass at region where

@@

\begin{deluxetable*}{ccccccc}
\tablecolumns{7}
\tablewidth{0pt}
\tablecaption{The host inference of CID1174} 
\tablehead{ 
\colhead{PSF rank} &
\colhead{total $\chi ^2$} & 
\colhead{weights $w_i$} &
\colhead{host flux (counts)} &
\colhead{host flux ratio}&
\colhead{\Reff (arcsec)}&
\colhead{\sersic\ $n$}
 \\ 
\colhead{(1)} &
\colhead{(2)} &
\colhead{(3)} &
\colhead{(4)} &
\colhead{(5)} &
\colhead{(6)} &
\colhead{(7)} 
} 
\startdata
%\multicolumn{5}{c}{Sample presented in \citet{Treu+07}}\\
%\\
1 & $8584.429$ & $1.000$ & $82.209$ & $35.4\%$ & $0\farcs{}345$ & $1.11$ \\
2 & $8646.711$ & $0.920$ & $99.102$ & $41.9\%$ & $0\farcs{}298$ & $1.93$ \\
3 & $8816.947$ & $0.734$ & $76.74$ & $33.0\%$ & $0\farcs{}365$ & $1.10$ \\
4 & $9304.841$ & $0.383$ & $128.618$ & $54.7\%$ & $0\farcs{}231$ & $2.78$ \\
5 & $9652.575$ & $0.241$ & $187.498$ & $79.0\%$ & $0\farcs{}116$ & $6.18$ \\
6 & $9917.101$ & $0.170$ & $100.166$ & $42.3\%$ & $0\farcs{}287$ & $2.07$ \\
7 & $10018.324$ & $0.148$ & $75.061$ & $32.3\%$ & $0\farcs{}365$ & $1.23$ \\
8 & $10087.456$ & $0.135$ & $79.835$ & $34.3\%$ & $0\farcs{}358$ & $1.20$ \\
\hline\\
Weighted value & & & $97.322\pm28.336$ & $41.5\%\pm11.7\%$& $0\farcs{}309\pm0\farcs{}065$  & $1.86\pm1.26$  \\
\enddata
\label{tab:weight_CID1174}
\tablecomments{
Column~1: Rank of the PSF from the library.
Column~2: Total $\chi ^2$ for the corresponding PSF.
Column~3: Weights for the inference.
Column~4-7: Fitted value for the host flux, host/total flux ratio, effective radius, and \sersic\ index.
For this sample, the inflation parameter $\alpha$ calculated by Eq.~\ref{eq:alpha} is 16.671.
}
\end{deluxetable*}

@@

\colhead{reduced $\chi ^2$}& \colhead{host-total flux ratio}& 

@@

\colhead{reduced $\chi ^2$}& \colhead{host-total flux ratio}& \colhead{magnitude} &

@@

CID1174 & $2.307$ & $42\%\pm12\%$ & $0\farcs{}31\pm0\farcs{}07$ & $1.9\pm1.3$ & $21.48\substack{+0.37\\-0.28}$ & $2.496$ & $11\%\pm1\%$ & $23.21\substack{+0.11\\-0.10}$ & $11.13\substack{+0.09\\-0.07}$ &$10.85\substack{+0.14\\-0.12}$\\
CID1281 & $1.322$ & $49\%\pm14\%$ & $0\farcs{}24\pm0\farcs{}09$ & $3.2\pm1.5$ & $22.88\substack{+0.36\\-0.27}$ & $1.378$ & $19\%\pm8\%$ & $24.83\substack{+0.60\\-0.38}$ & $10.49\substack{+0.09\\-0.07}$ &$10.21\substack{+0.13\\-0.12}$\\
CID206 & $2.054$ & $35\%\pm24\%$ & $0\farcs{}29\pm0\farcs{}15$ & $3.1\pm2.5$ & $21.82\substack{+1.30\\-0.58}$ & $1.903$ & $8\%\pm2\%$ & $23.67\substack{+0.40\\-0.29}$ & $10.95\substack{+0.32\\-0.14}$ &$10.66\substack{+0.34\\-0.18}$\\
CID216 & $1.514$ & $94\%\pm5\%$ & $0\farcs{}25\pm0\farcs{}06$ & $6.2\pm1.2$ & $21.51\substack{+0.05\\-0.05}$ & $1.425$ & $35\%\pm2\%$ & $23.45\substack{+0.05\\-0.05}$ & $11.13\substack{+0.02\\-0.02}$ &$10.85\substack{+0.1\\-0.1}$\\
CID237 & $2.349$ & $30\%\pm6\%$ & $0\farcs{}87\pm0\farcs{}17$ & $4.7\pm1.7$ & $21.28\substack{+0.26\\-0.21}$ & $2.354$ & $3\%\pm2\%$ & $23.72\substack{+1.04\\-0.52}$ & $11.26\substack{+0.07\\-0.05}$ &$10.98\substack{+0.12\\-0.11}$\\
CID255 & $1.625$ & $19\%\pm5\%$ & $0\farcs{}19\pm0\farcs{}06$ & $4.2\pm1.5$ & $21.61\substack{+0.37\\-0.28}$ & 2.858 & $4\%\pm2\%$ & $22.89\substack{+0.60\\-0.39} $& $11.17\substack{+0.09\\-0.07}$ &$10.89\substack{+0.14\\-0.12}$\\
CID3242 & $2.751$ & $46\%\pm13\%$ & $0\farcs{}20\pm0\farcs{}16$ & $6.1\pm1.9$ & $21.16\substack{+0.35\\-0.26}$ & $2.596$ & $5\%\pm1\%$ & $23.60\substack{+0.34\\-0.26}$ & $11.25\substack{+0.09\\-0.07}$ &$10.97\substack{+0.13\\-0.12}$\\
CID3570 & $1.665$ & $77\%\pm2\%$ & $0\farcs{}70\pm0\farcs{}01$ & $0.7\pm0.1$ & $21.16\substack{+0.02\\-0.02}$ & $1.332$ & $86\%\pm2\%$ & $22.97\substack{+0.01\\-0.01}$ & $11.07\substack{+0.01\\-0.01}$ &$10.79\substack{+0.1\\-0.1}$\\
CID452 & $1.684$ & $75\%\pm4\%$ & $0\farcs{}37\pm0\farcs{}02$ & $1.4\pm0.2$ & $21.18\substack{+0.06\\-0.06}$ & $1.452$ & $38\%\pm1\%$ & $22.73\substack{+0.02\\-0.02}$ & $11.21\substack{+0.02\\-0.02}$ &$10.93\substack{+0.1\\-0.1}$\\
CID454 & $2.203$ & $36\%\pm3\%$ & $0\farcs{}39\pm0\farcs{}02$ & $0.6\pm0.1$ & $21.20\substack{+0.08\\-0.07}$ & $1.291$ & $9\%\pm1\%$ & $23.35\substack{+0.06\\-0.06}$ & $11.19\substack{+0.02\\-0.02}$ &$10.91\substack{+0.1\\-0.1}$\\
CID50 & $5.576$ & $17\%\pm9\%$ & $0\farcs{}16\pm0\farcs{}11$ & $3.2\pm2.2$ & $20.93\substack{+0.86\\-0.48}$ & $4.940$ & $5\%\pm3\%$ & $22.50\substack{+1.15\\-0.55}$ & $11.15\substack{+0.22\\-0.12}$ &$10.87\substack{+0.24\\-0.16}$\\
CID543 & $1.902$ & $31\%\pm10\%$ & $0\farcs{}10\pm0\farcs{}00$ & $0.5\pm0.3$ & $21.99\substack{+0.41\\-0.30}$ & $1.435$ & $5\%\pm2\%$ & $23.77\substack{+0.53\\-0.36}$ & $10.79\substack{+0.1\\-0.07}$ &$10.51\substack{+0.14\\-0.12}$\\
CID597 & $1.565$ & $42\%\pm17\%$ & $0\farcs{}17\pm0\farcs{}06$ & $1.8\pm0.8$ & $21.87\substack{+0.54\\-0.36}$ & $1.254$ & $12\%\pm1\%$ & $23.56\substack{+0.13\\-0.11}$ & $10.81\substack{+0.14\\-0.09}$ &$10.53\substack{+0.17\\-0.13}$\\
CID607 & $1.692$ & $44\%\pm18\%$ & $0\farcs{}21\pm0\farcs{}09$ & $3.4\pm1.1$ & $21.19\substack{+0.58\\-0.37}$ & $2.590$ & $5\%\pm2\%$ & $23.57\substack{+0.51\\-0.35}$ & $11.10\substack{+0.14\\-0.09}$ &$10.82\substack{+0.18\\-0.14}$\\
CID70 & $2.041$ & $20\%\pm5\%$ & $0\farcs{}42\pm0\farcs{}10$ & $3.6\pm1.0$ & $21.86\substack{+0.30\\-0.24}$ & $2.361$ & $2\%\pm1\%$ & $24.63\substack{+0.68\\-0.41}$ & $11.07\substack{+0.08\\-0.06}$ &$10.79\substack{+0.13\\-0.12}$\\
LID1273 & $1.697$ & $53\%\pm9\%$ & $0\farcs{}30\pm0\farcs{}04$ & $1.2\pm0.5$ & $20.94\substack{+0.21\\-0.18}$ & $2.137$ & $6\%\pm1\%$ & $23.29\substack{+0.15\\-0.13}$ & $11.40\substack{+0.05\\-0.05}$ &$11.12\substack{+0.11\\-0.11}$\\
LID1538 & $2.362$ & $44\%\pm8\%$ & $0\farcs{}18\pm0\farcs{}04$ & $2.8\pm0.5$ & $21.25\substack{+0.22\\-0.18}$ & $2.173$ & $8\%\pm1\%$ & $23.09\substack{+0.19\\-0.16}$ & $11.21\substack{+0.06\\-0.05}$ &$10.93\substack{+0.11\\-0.11}$\\
LID360 & $3.918$ & $18\%\pm2\%$ & $0\farcs{}63\pm0\farcs{}02$ & $0.8\pm0.4$ & $21.46\substack{+0.14\\-0.12}$ & $4.914$ & $4\%\pm1\%$ & $23.25\substack{+0.17\\-0.15}$ & $11.17\substack{+0.04\\-0.03}$ &$10.88\substack{+0.11\\-0.1}$\\
